Revisiting the Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation using complex Empirical Orthogonal Functions

### 2021-08-17 analysis/paper/shceof.Rmd
Pequeños cambios

```{r setup, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE,
  comment = "#>",
  cache.extra = 42,
  cache.path = "../cache/paper/",
  fig.path = "../figures/",
  dpi = 300,
  dev = c("pdf", "png")
)

@@

@@

```{r test-irlba}
has_irlba <- requireNamespace("rilba", quietly = TRUE)
if (has_irlba) {
  stop("If installed, metR::EOF uses irlba, but that package has a bug with complex matrices\n(see: https://github.com/bwlewis/irlba/issues/55). Uninstall irlba with renv::remove(\"irlba\") and try again.")
}

@@

equation <- latex2exp::TeX(paste0("$\\mathrm{ONI} = ", 
                                  signif(coef(cos_model)[1], 2), "\\sin{(\\mathrm{phase})}$"),
                           output = "text")

@@

equation <- latex2exp::TeX(paste0("$\\mathrm{Precipitation}_{\\mathrm{West Australia}} = ", 
                                  signif(coef(model)[1], 2), "\\sin{(\\mathrm{phase})} + ", 
                                  signif(coef(model)[2], 2), "\\cos{(\\mathrm{phase})}$"), 
                           output = "text")

>>>>

```{r setup, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE,
  comment = "#>",
  cache.extra = 45,
  cache.path = "../cache/paper/",
  fig.path = "../figures/",
  dpi = 300,
  dev = c("pdf", "png")
)

@@

f <- formals(geom_contour_tanaka)
f$range <-  c(0.01, 0.2)
formals(geom_contour_tanaka) <- f

@@

```{r test-irlba}
has_irlba <- requireNamespace("irlba", quietly = TRUE)
if (has_irlba) {
  stop("If installed, metR::EOF uses irlba, but that package has a bug with complex matrices\n(see: https://github.com/bwlewis/irlba/issues/55). Uninstall irlba with renv::remove(\"irlba\") and try again.")
}

@@

equation <- latex2exp::TeX(paste0("$\\mathrm{ONI} = ", 
                                  signif(coef(cos_model)[1], 2), "\\sin{(\\mathrm{phase})}$"),
                           output = "character")

@@

equation <- latex2exp::TeX(paste0("$\\mathrm{Precipitation}_{\\mathrm{West Australia}} = ", 
                                  signif(coef(model)[1], 2), "\\sin{(\\mathrm{phase})} + ", 
                                  signif(coef(model)[2], 2), "\\cos{(\\mathrm{phase})}$"), 
                           output = "character")
